Radio Emission from Red-Giant Hot Jupiters

### 2015-09-22 ms.tex
changed the order of section 2 so that commonly-used framework comes first and original views come later; let me know if you prefer the previous one

Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify some ingredients. 
The property of the planetary magnetic field is described in \S\ref{ss:magneticfield}, and the stellar wind of the evolved stars is discussed in \S\ref{ss:stellarwind}.  
In \S\ref{ss:ionization}, we consider the ionization around the planets because it is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind. 
Then, we proceed to the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions for Planetary Magnetic Field}
\label{ss:magneticfield}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We estimate the planetary magnetic field of general planets  
simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below. 
% we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions for Stellar Wind}
\label{ss:stellarwind}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ionization around the planet}
\label{ss:ionization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
%\memoDS{We should write the expression ... it's just the quadratic formula, but it would be useful to write.}
When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_J$),  the solution is simply
%%%%%%%%%
\begin{eqnarray}
x[r] &=& \frac{-1 + \sqrt{1+4C[r]}}{2C[r]} \\
C[r] &\equiv &   \frac{4 \pi n \beta [T_e] r^2}{\dot{N} \sigma_H[E_{\rm photon}]}  \end{eqnarray}
%%%%%%%%%
The solid lines show the ionization fraction of $\xi=0$ (no additional ionization by electrons) and dashed lines show that of $\xi=0.5$. In the figure, the vertical lines show the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below. 
While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation (\ref{eq:sigma_H})) leads to the decrease in the radius of ionized region. 
Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{ionizationfraction.pdf}
   \caption{Profile of ionization fraction due to X-ray from the planetary accretion disk, measured from the surface of the planet. Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $\xi=0.8$. The vertical arrows show the Str\"omgren radius estimated simply  by equation (\ref{eq:stromgren}). The dotted vertical lines indicate the location of the magnetic stand-off radii, $r_{\rm mag}$,  obtained by equation (\ref{eq:stand-off-radius}) below. }
   %\memoDS{This looks great.  Might be good to also show the locations of the magnetic standoff point and the ``stromgren sphere radius'' on this figure (say, with vertical dashed and dotted lines?), and to move the legend to the lower left corner? {\tt plt.legend(loc=3)}}
  \label{fig:ionizationfraction}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Frequency of Radio Emission}
\label{ss:model_frequency}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Planetary auroral radio wave are emitted at the local cyclotron frequency along the motion of the plasmas.
The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $\nu_{\rm cyc}$: 
%%%%%%%%%% 
\begin{equation}
\nu_{\rm cyc} = \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
\end{equation}
%%%%%%%%%%
where $e$ and $m_e$ are the charge and mass of the electron, respectively.

Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $\nu_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $\nu_{\rm plasma}^{\rm los}$.
The plasma frequency may be expressed as
\begin{eqnarray}
\nu_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
 & = & 8979 {\rm~Hz} \times \left( \frac{n_e}{\rm cm^{-3}} \right)^{1/2} \, .
\label{eq:fplasma}
\end{eqnarray}
In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $\nu_{\rm plasma}^\oplus \lsim 10$~MHz.
At the favorable viewing condition, when the planet is on the near side of its star to the Earth, the maximum plasma frequency along the line of sight corresponds to that in the vicinity of the planet.
Therefore, combining Eq.~(\ref{eq:n_normalized}) and Eq.~(\ref{eq:fplasma}), we have
%%%
\begin{eqnarray}
\label{eq:fplasmalos} \nu_{\rm plasma}^{\rm los} & \sim & 
8979 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
\label{eq:fplasmalos_scaled} &=& 12 {\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
 & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \, .
\end{eqnarray}
%%%
%where in Eq.~(\ref{eq:fplasmalos_scaled}) we have taken the solar mass-loss rate $\dot M_\odot$ to be $2.0 \times 10^{-14}~M_\odot$/yr and the typical solar wind velocity $v_{\odot }$ to be 400~km/sec.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Flux of Radio Emission}
\label{ss:model_intensity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radiometric Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_{\rm mag} ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\bot }^2 r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
\end{eqnarray}
%%%
where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_{\rm mag}$ is the radius of the magnetic stand-off point. 
%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.

The radius of the magnetic stand-off point, $r_{\rm mag}$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
%%%
\begin{equation}
m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_{\rm mag}}{R_p} \right)^{-6}  \label{eq:stand-off}
\end{equation}
%%%
The radius obtained for Jupiter from this equality is about half of the actual magnetospheric radius \citep[][]{griesmeier2005}. 
By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
%If the radius of magnetosphere is estimated by scaling that of Jupiter according to equations (\ref{eq:n}) and (\ref{eq:stand-off}), 
%We estimate $r_{\rm mag}$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
%%%
\begin{eqnarray}
\nonumber r_{\rm mag} 
%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
&=& r_{mag,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{v}{v_{\odot }} \right)^{-1/6} \\
\nonumber &=& 15 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{v}{10^{-1}v_{\odot }} \right)^{-1/6}
 \label{eq:stand-off-radius}
\end{eqnarray}
%%%

%Thus, the radio emission, $P_{\rm radio}$, or equivalently the input kinetic energy, $P_{\rm k,\,inp}$, are estimated with $n$, $v$, and $\mathcal{M}$, which should be specified by assuming the properties of the stellar wind and the planetary magnetic field. 
%In the following, we describe our assumptions for these properties.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimate of Planetary Magnetic Field and Maximum Frequency}
\label{ss:Bplanet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{fig1_linear.pdf}
%   \caption{Radius and average density of the dynamo region as a function of planetary mass. }
   \plotoneh{fig2_Christensen.pdf}
   \caption{Upper panels: Radius and average density of the dynamo region as a function of planetary mass. Lower panels: Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
  \label{fig:planetaryB}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Figure \ref{fig:planetaryB} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region as function of planetary mass, as well as the heat flux at the outer boundary of the core, the estimated strength of planetary magnetic field $B$ and the corresponding cyclotron frequency ($\nu_{\rm cyc}$) as functions of planetary mass and the age. 
%Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
Reasonably, the resultant values agree with \citet{reiners2010}, who adopted the same scaling law for planetary magnetic field; we show this figure just for completeness.

%%%%%%%%%% 
%\begin{eqnarray}
%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
%\end{eqnarray}
%%%%%%%%%%
%under this model. 
Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz ($\sim $ the plasma cut-off frequency of Earth's ionosphere) and 1~GHz. 
In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
LOFAR, HERA, SKA, and potential upgrades to the VLA.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimate of Radio Intensity of RGHJs in comparison with canonical HJs}
\label{ss:brightness}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Based on the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows:
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_{\rm mag}^2 %= n v^3 \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/3} R_J^2  \\
\\
&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
\end{eqnarray}
%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radio Flux from Nearby M giants}
\label{ss:actualMgiants}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Detectability with Current and Near Future Low Frequency Radio Instrumentation}
\label{ss:detectability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In this section, we describe our scheme to estimate radio emission from RGHJs. 
First, we introduce our framework to compute the frequency and intensity of planetary radio emission in Section \ref{ss:model_frequency} and Section \ref{ss:model_intensity}, respectively. 
Then, two ingredients for the framework--the strength of planetary magnetic field and the property of the stellar wind---will be presented in Section \ref{ss:magneticfield} and Section \ref{ss:stellarwind}, respectively. 
In Section \ref{ss:ionization}, we consider the ionization around the planets, which is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Frequency of radio emission}
\label{ss:model_frequency}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Planetary auroral radio wave are emitted at the local cyclotron frequency along the motion of the plasmas.
The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $\nu_{\rm cyc,\,max}$: 
%%%%%%%%%% 
\begin{equation}
\nu_{\rm cyc,\,max} = \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
\end{equation}
%%%%%%%%%%
where $B$ is the strength of magnetic field at the planetary surface, $e$ and $m_e$ are the charge and mass of the electron, respectively, and $c$ is the speed of light.

Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $\nu_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $\nu_{\rm plasma}^{\rm los}$: 
%%%%%%%%%% 
\begin{equation}
\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^\oplus \;\;\; \mbox{and} \;\;\; \nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}
\end{equation}
%%%%%%%%%%
The plasma frequency may be expressed as
\begin{eqnarray}
\nu_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
 & = & 8979 {\rm~Hz} \times \left( \frac{n_e}{\rm cm^{-3}} \right)^{1/2} \, .
\label{eq:fplasma}
\end{eqnarray}
In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $\nu_{\rm plasma}^\oplus \lsim 10$~MHz. 
On the other hand, the $\nu_{\rm plasma}^{\rm los}$ depends on the density of stellar wind particles around the planet, which will be specified in Section \ref{ss:stellarwind} below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Flux of radio emission}
\label{ss:model_intensity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radiometric Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_{\rm mag} ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\star\bot }^2 r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
\end{eqnarray}
%%%
where $n$ is the number density of the stellar wind, $v$ is the relative velocity of the stellar wind particles and the planet, $ B_{\star\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_{\rm mag}$ is the radius of the magnetic stand-off point. 
%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.

The radius of the magnetic stand-off point, $r_{\rm mag}$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
%%%
\begin{equation}
m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_{\rm mag}}{R_p} \right)^{-6}  \label{eq:stand-off} ,
\end{equation}
%%%
where $m_p$ is the proton mass. Thus, 
%%%
\begin{equation}
r_{\rm mag} \sim R_p \left( 8\pi m_p n \right) ^{-1/6} v^{-1/3} B^{-1/3} \label{eq:stand-off-radius} 
\end{equation}
%%%
The radius obtained for Jupiter from this equality is about half of the actual magnetospheric radius \citep[][]{griesmeier2005}. 
To estimate $r_{\rm mag}$ for RGHJs, we scale this radius according to the parameter dependence of equation~(\ref{eq:stand-off-radius}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions for planetary magnetic field}
\label{ss:magneticfield}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to obtain the frequency and the intensity of the radio emission, we need to compute the strength of the magnetic field at the planetary surface, $B$. 
We do so simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below. 
% we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions for stellar wind}
\label{ss:stellarwind}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ionization of stellar wind particles around the planet}
\label{ss:ionization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{ionizationfraction.pdf}
   \caption{Profile of ionization fraction due to X-ray from the planetary accretion disk, measured from the surface of the planet. Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $\xi=0.8$. The vertical arrows show the Str\"omgren radius estimated simply  by equation (\ref{eq:stromgren}). The dotted vertical lines indicate the location of the magnetic stand-off radii, $r_{\rm mag}$,  obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below. }
   %\memoDS{This looks great.  Might be good to also show the locations of the magnetic standoff point and the ``stromgren sphere radius'' on this figure (say, with vertical dashed and dotted lines?), and to move the legend to the lower left corner? {\tt plt.legend(loc=3)}}
  \label{fig:ionizationfraction}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
%\memoDS{We should write the expression ... it's just the quadratic formula, but it would be useful to write.}
When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_J$),  the solution is simply
%%%%%%%%%
\begin{eqnarray}
x[r] &=& \frac{-1 + \sqrt{1+4C[r]}}{2C[r]} \\
C[r] &\equiv &   \frac{4 \pi n \beta [T_e] r^2}{\dot{N} \sigma_H[E_{\rm photon}]}  \end{eqnarray}
%%%%%%%%%
The solid lines show the ionization fraction of $\xi=0$ (no additional ionization by electrons) and dashed lines show that of $\xi=0.5$. In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below. 
While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation (\ref{eq:sigma_H})) leads to the decrease in the radius of ionized region. 
Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Planetary magnetic field and frequency of radio emission}
\label{ss:Bplanet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[bhtp]
   \plotoneh{rho_r_dynamo.pdf}
%   \caption{Radius and average density of the dynamo region as a function of planetary mass. }
   \plotoneh{qBf_Christensen.pdf}
   \caption{Upper panels: Radius and average density of the dynamo region as a function of planetary mass. Lower panels: Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
  \label{fig:planetaryB}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Figure \ref{fig:planetaryB} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region as function of planetary mass, as well as the heat flux at the outer boundary of the core, the estimated strength of planetary magnetic field $B$ and the corresponding cyclotron frequency ($\nu_{\rm cyc}$) as functions of planetary mass and the age. 
%Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
Reasonably, the resultant values agree with \citet{reiners2010}, who adopted the same scaling law for planetary magnetic field; we show this figure just for completeness. 
%%%%%%%%%% 
%\begin{eqnarray}
%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
%\end{eqnarray}
%%%%%%%%%%
%under this model. 
Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz and 1~GHz. 
In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
LOFAR, HERA, SKA, and potential upgrades to the VLA.

Since $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^\oplus $, the radio emission will not be hindered by Earth's ionosphere cut-off. 
One the other hand, it may be interfered by the plasma cut-off of the stellar wind particles around the planet. 
The maximum plasma frequency along the line of sight, $\nu_{\rm plasma}^{\rm los}$, corresponds to that in the vicinity of the planet, if the planet is on the near side of its star to the Earth. Therefore, substituting equation~(\ref{eq:n_normalized}) to $n_e$ in equation~(\ref{eq:fplasma}), 
%%%
\begin{eqnarray}
\label{eq:fplasmalos} \nu_{\rm plasma}^{\rm los} & \sim & 
8979 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
\label{eq:fplasmalos_scaled} &=& 12 {\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
 & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \, .
\end{eqnarray}
We can see emission only from where $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$. Therefore, for Jupiter-mass planets, only distant ones at $\sim 5 $ AU or further, will emit the radio waves from the system. 
The detectable parameter space will be presented in more detail in the next section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Flux of RGHJ radio emission in comparison with canonical HJs}
\label{ss:brightness}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The magnetic stand-off radius (equation (\ref{eq:stand-off-radius})) may be written as follows using the stellar mass-loss rate: 
%%%
\begin{eqnarray}
\nonumber r_{\rm mag} 
%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
&=& r_{\rm mag,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{v}{v_{\odot }} \right)^{-1/6} \label{eq:stand-off-radius2}
\end{eqnarray}
%%%
The typical value for RGHJs is found by substituting relevant values for stellar wind parameters described in Section \ref{ss:stellarwind}:
%%%
\begin{eqnarray}
\nonumber r_{\rm mag} &\sim & 15 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{v}{10^{-1}v_{\odot }} \right)^{-1/6}
 \label{eq:stand-off-radius_RGHJ}
\end{eqnarray}
%%%

Substituting equation (\ref{eq:stand-off-radius2}) to equation (\ref{eq:Pinp_kin}), the scaling of the radio emission is expanded as follows:
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_{\rm mag}^2 %= n v^3 \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/3} R_J^2  \\
\\
&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
\end{eqnarray}
%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radio flux from nearby M giants}
\label{ss:actualMgiants}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Detectability with current and near future low frequency radio instrumentation}
\label{ss:detectability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
